Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-02 tex/sections/intro.tex
Fix some readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The most conventional use case of a blockchain is financial application. This makes the security of the consensus
protocol of a blockchain crucially important. Unfortunately, many currently used blockchains are vulnerable to a
certain type
of consensus attack, know as the bribery attack. In a bribery attack, an adversary tries to corrupt participants of a
protocol and make them violate the protocol by offering them money.

At the time of writing of this document,
the total mining reward for a bitcoin block is around \$150,000. If we assume that mining rewards define the utility
function of bitcoin miners accurately, one could hire all hashing power of the bitcoin network for one hour by spending
only \$750,000. The situation is not much different for PoS blockchains, as long as the total stake\footnote{Here, by
stake, we mean a real number measuring the total interest of a user in the system. We are not referring, in
particular, to the locked amount of a user's money that is known as stake in some PoS protocols.}
of validators is a relatively small value. This problem is more severe in blockchains that use randomly selected small
sets of validators. Selecting these random sets by hidden random procedures would not help, as long as the
validator himself knows he has been selected, before casting his vote.

It appears that the only solution to this important vulnerability is to effectively participate all the stake of the
system in the consensus protocol. This large participation secures the protocol against bribery or
collusion because the adversary would have to spend unrealistic amount of money to bribe enough users.

However, for effective participation in the consensus protocol, a validator needs to be able to detect
illegal transactions. Detecting illegal transaction can be done by accessing the ledger
state and executing transactions according to the protocol predefined rules. The
ledger state, even for small blockchains, could be several
hundreds of gigabytes, and executing transactions could easily become costly when a blockchain is acting as a
smart contract platform. This computational and storage overhead could prevent most of
ordinary users from any type of participation in the process of securing a blockchain.

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. A blockchain consensus protocol relies on a network of computers, not humans. Ordinary users use
simple and similar computer systems. That means, they all have similar vulnerabilities that could be used by an
adversary to attack the consensus protocol. For example, a malware might be
able to infect a lot of normal computers in the world, and then it might be used to hijack the majority of
participants in the consensus protocol and compromise the security of the blockchain. Securing a computer
system against cyberattacks needs planning ahead and access to engineering resources. Special software and hardware,
like custom-built operating systems and isolated specialized hardware would be required. This is not something a normal
user can do. Only powerful centralized entities that have enough financial and technical resources are able to build
systems that are resilient against sophisticated cyberattacks. So in this regard, a centralized system is arguably
superior to a decentralized \footnote{Note
that decentralized and distributed are two different concepts.} system.

To overcome these difficulties, Argennon uses a hybrid proof of stake consensus protocol. A small committee of
delegates is democratically elected
by the Argennon users and is responsible for minting new blocks of the Argennon blockchain. Each
minted block is required to get approved by its corresponding validator assembly. Assemblies are very large, and they
contain at least three percent of the total stake of the system. A block is approved if it gets approval votes of at
least \(2/3\) of the total stake of its validator assembly.

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
its ledger state. This set defines how
the ledger state of a block can be reached from the state of its previous block via a set of intermediate states.
Each CI statement defines an ordered list of transactions (called external requests in Argennon) and determines
the intermediate states before and after executing those transactions:
\[
    \tau_{(s_i,s_{i+1},\mathbb{R})} \coloneqq \text{``$s_{i+1}$ is the next state after executing external requests
        $\mathbb{R}$ on state $s_i$''}
\]
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements from the Argennon Publicly Verifiable Cloud. They can also receive the state of the previous
block (the required part of it) and proofs that show the received data is consistent with the previous block commitment.

Verifying a succinct proof can be exponentially faster than replaying the computation. Moreover, verifications of
different statements are independent and can be done in parallel. Therefore, a validator can use multiple cores for
verifying CI statements of a single block and different validator assemblies can simultaneously verify different blocks.
In addition, proof generation of different CI statements can be done in parallel similarly. However, for parallel
proof generation, the state transition needs to be known in advance. That's why in Argennon, delegates do not try
to generate proofs and focus all their computational power on executing requests and generating the state transition
as fast as possible.

>>>>

The most conventional use of blockchains is in financial applications. Therefore, the security level of the consensus
protocol of a blockchain has a crucial importance. Unfortunately, many currently used blockchains are vulnerable to a
certain type of consensus attack, know as the bribery attack. In a bribery attack, an adversary tries to corrupt
participants of a protocol and make them violate the protocol by offering them money.

At the time of writing of this document,
the total mining reward for a bitcoin block is around \$150,000. If we assume that mining rewards accurately define
the utility function of a bitcoin miner, one could hire all hashing power of the bitcoin network for one hour by
spending
only \$750,000. The situation is not much different for PoS blockchains, as long as the total stake\footnote{Here, by
stake, we mean a real number measuring the total interest of a user in the system. We are not referring, in
particular, to the locked amount of a user's money that is known as stake in some PoS protocols.}
of the validator set of a block is a relatively small value. This problem is more severe in blockchains that use
randomly selected small sets of validators, and selecting these random sets by hidden random procedures would not
help, since the validator himself knows he has been selected, before casting his vote.

It appears that the only solution to this important vulnerability is to effectively participate all the stake of the
system in the consensus protocol. This large participation makes the protocol resilient against bribery or
collusion because the adversary would have to spend unrealistic amount of money to bribe enough users.

However, for effective participation in the consensus protocol, a validator needs to be able to detect
illegal transactions. Detecting illegal transaction can be done by accessing the ledger
state and executing transactions according to the protocol defined rules. The
ledger state, even for small blockchains, could be several
hundreds of gigabytes, and executing transactions could easily become costly when a blockchain is acting as a
smart contract platform. This computational and storage overhead could prevent most of
ordinary users from any type of participation in the process of securing a blockchain.

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. A blockchain consensus protocol relies on a network of computers, not humans. Ordinary users use
simple and similar computer systems. That means, they all have similar vulnerabilities that could be used by an
adversary to attack the consensus protocol. For example, a malware might be
able to infect a lot of normal computers in the world, and then it could be used to hijack the majority of
participants in the consensus protocol and compromise the security of the blockchain. Securing a computer
system against cyberattacks needs planning ahead and access to engineering resources. Special software and hardware,
like custom-built operating systems and isolated specialized hardware would be required. This is not something a normal
user can afford. Only powerful centralized entities, having large financial and technical resources, could build
systems that are resilient against sophisticated cyberattacks. In this regard, we have to admit, a centralized system is
arguably superior to a decentralized \footnote{Note that decentralized and distributed are two different concepts.}
system.

To overcome these difficulties, Argennon uses a hybrid Proof of Stake consensus protocol. A small committee of
delegates is democratically elected
by the Argennon users and is responsible for minting new blocks of the blockchain. Each
minted block is required to get approved by its corresponding validator assembly. Assemblies are very large sets of
validators containing at least three percent of the total stake of the system. A block is approved if it gets
approval votes from at least \(2/3\) of the total stake of its validator assembly.

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
the corresponding ledger state of the block. This set defines how
the ledger state of a block can be reached from the state of its previous block via a set of intermediate states.
Each CI statement defines an ordered list of transactions (called external requests in Argennon) and determines
the intermediate states before and after executing those transactions:
\[
    \tau_{(s_i,s_{i+1},\mathbb{R})} \coloneqq \text{``$s_{i+1}$ is the next state after executing external requests
        $\mathbb{R}$ on state $s_i$''}
\]
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements from the Argennon Publicly Verifiable Cloud. They can also receive the state of the previous
block (the required part of it) and proofs that show the received data is consistent with the previous block commitment.

Verifying a succinct proof can be exponentially faster than replaying the computation. Moreover, verifications of
different CI statements are independent and can be done in parallel. Therefore, a validator can use multiple cores for
verifying CI statements of a single block and different validator assemblies can simultaneously verify different blocks.
In addition, proof generation of different CI statements can be done in parallel similarly. However, for parallel
proof generation, the state transition needs to be known in advance. That's why in Argennon, delegates do not try
to generate proofs and focus all their computational power on executing requests and generating the state transition
as fast as possible.
